---
####################################################################
#                     The tidyverse and beyond 
#                            Workshop 8
#                   Everything in its right place
#                        4th December 2017
#                  Worksheet C: R Markdown example
##################################################################
---

# By placing a hash symbol I have created this header

## Two hash symbols gives me a second header

### And so on

Now I am just writing my text as though I am in a MSWord document. I don't need to worry about keeping the sentances short like in the R scripts or starting each sentance with a #.

*I can put text in italics* or **I can put text in bold**

You have a lot of options available to you, and the documentation is out there to help you. 
For example, this is how to write in superscript^2^. This is written in subscript~2~.

These are just a few of options available.

To learn more visit [the R Mrakdown webpage](http://rmarkdown.rstudio.com/)



### Tables
Simple tables are straightforward to generate

**Table 1.**  Summary data of the iris data set

Data | `r colnames(iris[1])` | `r colnames(iris[2])`
------|--------|--------
Number of data points | `r nrow(iris)` | `r nrow(iris)`
Mean | `r mean(iris[,1])` | `r mean(iris[,2])`
Median | `r median(iris[,1])` | `r median(iris[,2])`
Std dev | `r sd(iris[,1])` | `r sd(iris[,2])`

There are packages out there that make this process easier. For example, pander will take the output of a linear model and give a more presentable table. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(pander)
```

## An example using life expectancy data over time for Ireland
Let's create a plot and a table of the linear model

```{r plot of Irish data, echo=FALSE}
library(gapminder)
ire <‐ filter(gapminder, country == "Ireland")
ire %>%
ggplot(aes(year, lifeExp)) +
geom_line() +
ggtitle("Full data = ")
ire_mod <‐ lm(lifeExp ~ year, data = ire)

pander(summary(ire_mod))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
